%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% tbonza - One Page moderncv resume
% LaTeX Template
% Version 1.0 (11/15/2015)
%
% Original Author
% Tyler Brown (http://tbonza.github.io/)
%
% Original Repository
% https://github.com/tbonza/Smaller-Projects/tree/master/resume
%
% MIT License
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[10pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
\moderncvtheme[blue]{classic}
\usepackage[scale=.77]{geometry}

% personal data
\firstname {Tyler}
\lastname {Brown}
\address {349 Linwood Ave}{Newton, MA, 02460}
\phone {+1~(603)~321~3097}
\email {tylers.pile@gmail.com}
\social [github]{tbonza}


\begin{document}
\makecvtitle
\section{Summary}
{A skilled analyst, experienced in solving data problems and statistical
  modeling, who synthesizes information to tell a story that contributes
  value.}
\section{Experience}
\cventry {2014-Present}{Senior Research Data Analyst}
         {GreenZone Solutions, Inc.}
         {\textit{(EMM Group, Northeastern University)} Boston, MA}
         {}{Contributes to the development of experimental
           mapping methodology as a member of the EMM group at
           Northeastern University. The methodology developed within
           this group contributes to multiple Agencies and Countries
           working to further security interests of the United States.
           \newline
           \begin{itemize}
           \item Certain tools and techniques developed here are
             considered proprietary and subject to a non-disclosure
             agreement.
           \item Python, R, SQL, Regular expressions, and Java used for
             statistical analysis.
           \end{itemize}
         }

\cventry {2013-2014}{Data Analyst}
         {Recommind, Inc.}
         {Norwood, MA}
         {}{Processed electronically stored information (ESI) for
           upload into the data review platform.
           \newline
           \begin{itemize}
           \item Use of SQL, regular expressions, and shell scripting
             to process CSV data used in legal cases.
           \item Helped train new hires.
           \item Use of Python to create custom scripts that resolved
             unique data problems.
           \end{itemize}}

\cventry {2012-2013}{Analyst}
         {Evolution Enterprises, Inc.}
         {\textit{(US Army RDECOM Contracting Center - Natick Contracting Division)} Natick, MA}
         {}{Assisted the U.S. Army with contract procurement and
           production of organziational analytics.
           \newline
           \begin{itemize}
           \item Partnered with government personnel to reconcile
             \$75 billion in contract allocations with over \$1.5
             billion in contract modifications using SQL database
             skills in Microsoft Access; among other data projects.
         \end{itemize}}

\section{Technical Skills}
{\begin{description}      
\item[Business Tools] MS Office
\item[Data Tools] Datameer, Platfora, Python, R, Regular Expressions,
  Shell Scripting, SPSS, SQL, Stata, 
\end{description}}

         
\section{Education}
\cventry {2010-2012}{M.A. Political Science}{SUNY-Binghamton}
         {}{}{Binghamton University’s Department of
           Political Science is ranked in the top 20 by the
           2010 NRC Study, and 19th in the world by the Hix study}
         
\cventry {2006-2010}{B.A. Political Science}{Franklin Pierce University}
         {}{}{}


\section{Clearances}
DHS Public Trust
         
\end{document}
